\documentclass{subfiles}

\begin{document}
	\par Remote sensing refers to the acquisition of information about objects, {\color{blue} for example} vegetation and archaeological monuments, without physical contact and the subsequent interpretation of that information.  The sensors used to capture the information are divided into passive and active. For example satellite photography is passive because information are collected from the {\color{blue} reflected natural} sun light, while Airborne Laser Scanners (ALS) are active because they emit laser beams and collects information from the backscattered laser energy~\cite{Smith2012}.
	
	\par According to Wanger et al, Airborne Laser Scanning (ALS) is a growing technology used in environmental research to collect information about the Earth, such as vegetation and tree species. Comparing ALS with traditional photography, {\color{blue} ALS is not influenced by light and it is therefore less dependent on weather conditions (ie. it collects information from below the clouds, or at night)}. The laser beam also partially penetrates the tree canopies {\color{blue} allowing it to record} information about the forest structure below the canopy, as well as the ground ~\cite{Wanger2004}. {\color{blue}ALS methods are divided into pulse systems, which repeatedly emit pulses, and continuous wavelength systems that continuously emit light. They both acquire information from the backscattered laser intensity over time, but continuous wavelength systems are more complicated because they obtain one extra physical parameter, the frequency of the ranging signal}. Further, according to Wehr and Lohr, continuous wavelength systems are 85 times less accurate than pulse systems ~\cite{Wehr1999}.
	
	\par {\color{blue} LiDAR (Light Detection And Ranging) systems are active and pulse laser scanning systems ~\cite{Wehr1999}. They are divided into two groups according to the diameter of the footprint left by the laser beam on the ground, which is primarily dependent on the distance between the sensor and the target (altitude, in most remote sensing) and the beam divergence. The small-footprint group has a 0.2-3m diameter, is widely commercialised and the sensors are mostly carried on planes (ALS systems). In contrast, the large-footprint systems have a wider diameter (10-70m) and during experiments they were mostly mounted on satellites. Small-footprint systems record at higher resolution but cannot guarantee that every pulse will reach the ground due to the small diameter of their footprint, making topographic measurements difficult, and are limited to smaller survey areas due to the cost and availability of aircraft. In contrast, large-footprint scanners have wider diameters and can therefore scan wider areas with the likelihood of recording the ground to be higher ~\cite{Mallet2009} }. 
	
	\par In addition, there are two types of LiDAR data: discrete and full-waveform (FW). {\color{blue} Discrete LiDAR records a few peaks of the reflected laser intensity, while FW LiDAR stores the entire backscattered signal}. The discrete LiDAR has been widely used and a 40\verb|%| reduction of fieldwork has been achieved at Interpine Ltd Group, New Zealand, with that technology. Regarding the newer FW LiDAR, scientists understand their concepts and potentials but due to the shortage of available tools able to handle these large datasets, there are very few uses of FW LiDAR ~\cite{Anderson2015}. 
	
	\par  The design of the first FW LiDAR system was introduced in 1980s, but the first operational system was developed by NASA in 1999~\cite{Chauve2007}. The vastly increased amount of information recorded within the FW LiDAR suggests many new possibilities and problems from the point of view of image understanding, remote surveying and visualisation. As an indication, a 9.3GB discrete LiDAR from New Forest, UK, corresponds to 55.7GB of FW LiDAR. 
	
	{\color{blue} This research is focused on the representation and efficient use of FW LiDAR data and contributes both to forestry visualisations and classifications. Two datasets are used for testing and evaluation: the New Forest and the RedGum dataset. An in-depth explanation of LiDAR systems and the specifications, differences and challenges of the two datasets are given in Section \ref{AcquireData}. An overview of the specific aims, objectives and contributions of this thesis, set in the context of these datasets, is then given at Section \ref{PipeLine}. }
	    
\end{document}
